---
title: "Steam Review Data Cleanup Log"
author: "Mike Kazantsev"
version: 1.0
date: '2022-05-10'
output: html_document
---

## Cleaning up and checking datasets

Review datasets were created using Steam API. First I'll check if all reviews
up to date were actually downloaded and if there are any reviews with completely
empty data (since Steam allows the free format of Review text it's quite 
possible there are reviews not containing any coherent text, but we'll check
it later.

## TODO:

* streamlining cleaning to allow multiple appids in one run
* full automation

## Loading necessary packages

-   tidyverse
-   lubridate

```{r loading libraries}
library(tidyverse)
library(lubridate)
library(dplyr)
library(pwr)
library(readr)
```

## Setting variables
```{r setting variables}

appid <- 1889981

```

## Loading dataset

```{r loading datasets}
#overall game data
game_summary <- read_csv("data/steamapps.csv")
#reviews summary and reviews
dataset_summary <- read_csv(paste("data/summary_",appid,".csv", sep = ""))
dataset_reviews <- read_csv(paste("data/review_",appid,".csv", sep = ""),
                        col_types=cols(author.steamid = col_character()),
                        )
```

## Cleaning up and checking datasets

### Game dataset

```{r}
str(game_summary)
```

This dataset doesn't need much work - changing release_date to the proper date
format and transforming developers/publishers/categories/genres into the list
of strings

```{r cleaning up game summary dataset}
game_summary_cleaned <- game_summary %>% 
  mutate(release_date = as.Date(release_date, format = "%d %b, %Y"),
         developers = strsplit(developers,split='\\|'),
         publishers = strsplit(publishers,split='\\|'),
         categories = strsplit(categories,split='\\|'),
         genres = strsplit(genres,split='\\|')
         )
```

### CK3 Base game dataaset

```{r}
str(dataset_reviews)
```

Checking if there are reviews that were not downloaded successfully and the
positive/negative difference by comparing with summary dataset:

```{r}
cat("Total reviews: ",dataset_summary$total_reviews,"\n")
cat("Not downloaded reviews: ",
    dataset_summary$total_reviews - nrow(dataset_reviews) %>% abs,"\n")
dataset_missing_positives <- dataset_reviews %>% 
      filter(voted_up == TRUE) %>% 
      nrow - dataset_summary$total_positive
cat("Missing positive reviews: ", dataset_missing_positives %>% abs, "\n")
dataset_missing_negatives <- dataset_reviews %>% 
      filter(voted_up == FALSE) %>% 
      nrow - dataset_summary$total_negative 
cat("Missing negative reviews: ", dataset_missing_negatives %>% abs, "\n")
```

Checking for the duplicates by review_id and author.steamid:

```{r}
cat("Downloaded reviews: ", nrow(dataset_reviews), "\n")
cat("Unique review authors:", length(unique(dataset_reviews[["author.steamid"]])), "\n")
cat("Unique reviews (by ID):", length(unique(dataset_reviews[["review_id"]])), "\n")
cat("Unique review texts:", length(unique(dataset_reviews[["review_text"]])), "\n")
```

Checking null values:

```{r}
dataset_reviews %>% summarise(across(everything(), ~ sum(is.na(.))))
```

Checking how many reviewers didn't have playtime:

```{r}
cat("Players that don't have playtime:", dataset_reviews %>% 
      filter(author.playtime_forever < 1) %>% nrow, "\n")
```

Removing reviews from the same authors, leaving the newest version (Since the
review texts are in free form, removing duplicates/empty texts at this stage is
not useful as we can use these reviews for analysis anyways). We also change
timestamp to the datetime:

```{r}
dataset_reviews_cleared <- dataset_reviews %>% 
  group_by(author.steamid) %>% 
  slice(which.max(timestamp_created)) %>% 
  mutate(timestamp_created = as.POSIXct(timestamp_created,
                                        tz="GMT",
                                        origin="1970-01-01"),
         timestamp_updated = as.POSIXct(timestamp_updated,
                                        tz="GMT",
                                        origin="1970-01-01"))

cat("Unique review authors",
    length(unique(dataset_reviews_cleared[["author.steamid"]])), "\n")
```

Saving the resulting dataset:
``` {r}
#For Windows, R 4.2.0+ is advised, otherwise UTF encoding might break
dataset_reviews_cleared %>%
   write.csv(paste0(c("data-clean/",appid,".csv"), collapse=""),
             fileEncoding = "UTF-8")
```