---
title: "Steam Review Data Analysis Log - One DLC"
author: "Mike Kazantsev"
date: '2022-05-10'
output: html_document
---

## Loading necessary packages

-   ggplot2
-   dplyr
-   lubridate
-   tidyverse
-   tidytext
-   tidiyr
-   stopwords
-   scales
-   stringr
-   sentimentr
-   ggwordcloud

Setting up environment and loading necessary packages

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(tidytext)
library(stopwords)
library(lubridate)
library(scales)
library(stringr)
library(tidyr)
library(sentimentr)
library(ggwordcloud)
```

## Reorganizing datasets

First, I'll merge the base game and the DLC review datasets so that it'll be
easier to use aggregation functions and show the results of analysis in charts.

```{r, Loading-and-cleaning-up-datasets}
#Loading datasets
#For Windows, R 4.2.0+ is adviced, otherwise UTF encoding might break
#ck3 review reviews 
basegame_cleared <- read_csv("data/basegame_cleared.csv", col_types=cols(
  author.steamid = col_character(),
  timestamp_created = col_datetime(format = ""),
  timestamp_updated = col_datetime(format = "")))
#ck3 DLC reviews
dlc_cleared <- read_csv("data/dlc_cleared.csv", col_types=cols(
  author.steamid = col_character(),
  timestamp_created = col_datetime(format = ""),
  timestamp_updated = col_datetime(format = "")))

#Adding the game name column we'll be aggregating with later

basegame_cleared$game <- "Crusader Kings III"
dlc_cleared$game <- "Crusader Kings III: Royal Court"

reviews_cleared <- rbind(basegame_cleared, dlc_cleared)
#Let's spread the author.playtime_forever, author.playtime_last_two_weeks,
#author.playtime_at_review, author.last_played from the base game to the dlc 
#when it's possible:

reviews_cleared <- reviews_cleared %>% 
  group_by(author.steamid) %>% 
  mutate(author.playtime_forever = max(author.playtime_forever)) %>% 
  mutate(author.playtime_last_two_weeks = max(author.playtime_last_two_weeks)) %>% 
  mutate(author.playtime_at_review = max(author.playtime_at_review)) %>% 
  mutate(author.last_played = max(author.last_played)) %>% 
  ungroup() %>% 
  select(-1)
```

## Analyzing review rates

### High weighted reviews

Let's start with something simple: positive/negative reviews proportions fo
r base game and DLC: Positive/negative percentages for the high weighted score 
(Filtered out weighted score below 0.5, determines review's helpfulness)

```{r High-weighted-review-plot, warning=FALSE}
#High weighted reviews
plot1_data <- reviews_cleared %>% 
  filter(weighted_vote_score > 0.5) %>% 
  group_by(game) %>% 
  mutate(review_count = n()) %>% 
  ungroup() %>% 
  group_by(game, voted_up, review_count) %>% 
  summarize(
    review_voted = n(),
  ) %>% 
  as_tibble() %>% 
  mutate(percentage = review_voted/review_count) %>% 
  select(game, voted_up, percentage)
  #Putting the plot
```
```{r plot1, fig.width = 5, fig.height = 5}
ggplot(data = plot1_data, aes(x = game, y  = percentage, fill = factor(voted_up))) + 
  geom_col(
    position="stack") +
  labs(
    x = "Game",
    y = "Percentage",
    title = "Review rates for high weighted reviews",
    subtitle = "Positive/negative review rates for high weighted reviews",
    caption =paste0(strwrap("Reviews having weight score above 0.5 were considered as high weighted", 40),
                    collapse="\n"),
  ) + 
  scale_fill_discrete(name = "Review:", labels=c("Negative", "Positive")) + 
  scale_y_continuous(labels=scales::percent) + 
  #Adding labels
  geom_text(
    aes(label = percent(percentage,accuracy = 0.01)),
    position = position_fill(vjust = 0.5),
    size = 3
  ) + 
  scale_x_discrete(labels = (\(x) gsub("([^\\s]+\\s[^\\s]+)\\s","\\1\n",x,perl=TRUE))) + 
  theme(axis.text.x = element_text(vjust = 0.5, hjust=0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

### Review changes by date

Review changes for game and DLC by date:

```{r, Review-rate-by-date-plot, warning=FALSE}
#Regrouping data and getting percentages of positive/negative reviews for each title/date
#Getting chart data
reviewsbydate_chart_data <- reviews_cleared %>%
  mutate(date = floor_date(timestamp_created,"month")) %>%
  group_by(date, game) %>% 
  mutate(review_count = n()) %>% 
  ungroup() %>% 
  group_by(date, game, voted_up, review_count) %>% 
  summarize(
    review_voted = n(),
  ) %>% 
  as_tibble() %>% 
  mutate(percentage = review_voted/review_count) %>% 
  select(date, game, voted_up, percentage)
#Making chart labels
reviewsbydate_chart_text <- reviewsbydate_chart_data %>% 
  group_by(game,voted_up) %>% 
  filter((percentage >= max(percentage) | percentage <= min(percentage)) 
         & voted_up == TRUE) %>% 
  mutate(label=ifelse(percentage == max(percentage),
                      paste0("Max rate - ",percent(percentage,accuracy = 0.01)),
                      paste0("Min rate - ", percent(percentage,accuracy = 0.01)))) %>% 
  ungroup
#Filling out the plot
reviewsbydate_chart_data %>% 
  filter(voted_up == TRUE) %>% 
  ggplot(aes(x = date, y  = percentage, fill=game)) + 
  geom_area(stat="identity", position=position_dodge(width = 0.1)) +
  labs(
    x = NULL,
    y = NULL,
    title = "Positive reviews %",
    subtitle = "By date for the base game and the DLC"
  ) +
  scale_fill_discrete(name = "Game:") + 
  scale_y_continuous(labels=scales::percent) + 
  geom_text(data = reviewsbydate_chart_text,
            aes(label = label),
            check_overlap = TRUE,
            vjust="inward",
            hjust="inward",
            size = 4
  ) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "bottom") +
  scale_x_datetime(date_breaks = "1 month", date_labels="%b %y")

```

### Opinion changed between the base game and the DLC

As we can see, there is a significant difference between the base game reviews
and DLC reviews, and the base game has much more positive reviews even after
the DLC release. So we can assume the players are unhappy with the DLC itself,
not the game after it's release (although there is some drop in positive reviews
for the base game as well). Let's see how reviews change for players that
reviewed both base game and the DLC:

```{r, Opinion-changes, warning=FALSE}
#filtering data
reviews_cleared %>% 
  group_by(author.steamid) %>% 
  filter(n() == 2) %>% 
  select(author.steamid,game,voted_up) %>% 
  spread(game,voted_up) %>% 
  #grouping up and  getting percentages
  mutate(Vote_change = case_when(
    (`Crusader Kings III` & `Crusader Kings III: Royal Court`) ~ "Remained positive",
    (`Crusader Kings III`==TRUE & `Crusader Kings III: Royal Court`==FALSE) ~ "Changed from positive to negative",
    (`Crusader Kings III`==FALSE & `Crusader Kings III: Royal Court`==TRUE) ~ "Changed from negative to positive",
    (`Crusader Kings III`==FALSE & `Crusader Kings III: Royal Court`==FALSE) ~ "Remained negative",
  )) %>%
  group_by(Vote_change) %>% 
  summarise(count = n()) %>% 
  mutate(Percentage = count/sum(count)) %>% 
  #making plot
  ggplot(aes(x=Vote_change, fill = Vote_change, y = Percentage)) + 
  geom_col() + 
  geom_text(aes(label = percent(Percentage)), vjust = -0.25) +
  scale_fill_discrete(name = "Rate changes:") +
  scale_y_continuous(labels=scales::percent) + 
    labs(
    title = "Vote rate changes",
    subtitle = "Reviewers changed their opinion between the base game and the DLC",
    caption = "1607 out of 3644 reviewers reviewed both base the game and the DLC"
  ) + 
  annotate(geom = "text",
           x = "Changed from positive to negative",
           y = 0.4,
           label = paste0(strwrap("A third of the players has changed the opinion", 40),
                          collapse="\n"),
           size = 4) +
  scale_x_discrete(labels = (\(x) gsub("\\s","\n",x))) + 
  theme(axis.text.x = element_text(vjust = 0.5, hjust=0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

It seems my assumption was correct - a third of the players has changed their
opinion to the negative between the base game and the DLC.

### Reviews by playtime

Sadly, it is impossible to track the time played for the DLCs - this data is
only available to the game. Nevertheless, we may take a look at the difference
of the game perception between the long-standing players and the new ones.

```{r, Reviews-by-playtime, warning=FALSE}
#grouping up and  getting percentages
#% of DLC reviewers not reviewed the base game
not_reviewed_basegame <- reviews_cleared %>% 
  filter(author.playtime_forever == 0) %>% 
  nrow()/nrow(reviews_cleared %>% filter(game =="Crusader Kings III: Royal Court"))
#% of DLC reviewers played 50 hours and more
longplayed_reviewers <- reviews_cleared %>% 
  filter(author.playtime_forever >= 3000 & game == "Crusader Kings III: Royal Court") %>% 
  nrow()/nrow(reviews_cleared %>% filter(game =="Crusader Kings III: Royal Court"))

reviews_cleared %>%
  mutate(playtime_group = case_when(
           (author.playtime_forever == 0) ~ "Didn't review the base game",
           (author.playtime_forever < 600 & author.playtime_forever > 0) ~ "Less than 10 hours played total",
           (author.playtime_forever < 3000 & author.playtime_forever >= 600) ~"Between 10 and 50 hours played total",
           (author.playtime_forever >= 3000) ~"100 and more hours played total")) %>%
  group_by(playtime_group, game) %>% 
  mutate(review_count = n()) %>% 
  ungroup() %>% 
  group_by(playtime_group, game, voted_up, review_count) %>% 
  summarize(
    review_voted = n(),
  ) %>%
  as_tibble() %>% 
  mutate(percentage = review_voted/review_count) %>% 
  select(playtime_group, game, voted_up, percentage) %>% 
  #Putting the plot
  ggplot(aes(x = playtime_group, y  = percentage, fill = factor(voted_up))) + 
  geom_col(
    position="stack") +
  labs(
    x = "Playtime",
    y = "Percentage",
    title = "Reviews by playtime",
    subtitle = "Review rates for different playtimes",
    caption = paste0(percent(not_reviewed_basegame, accuracy = 0.01)," reviewers only reviewed the DLC")
  ) + 
  scale_fill_discrete(name = "Review:", labels=c("Negative", "Positive")) + 
  scale_y_continuous(labels=scales::percent) + 
  #Adding labels
  geom_text(
    aes(label = percent(percentage,accuracy = 0.01)),
    position = position_fill(vjust = 0.5),
    size = 3
  ) + 
  scale_x_discrete(labels = (\(x) gsub("([^\\s]+\\s[^\\s]+)\\s","\\1\n",x,perl=TRUE)))  + 
  theme(axis.text.x = element_text(vjust = 0.5, hjust=0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~game, ncol = 1)

```
Interestingly, the players that have played the game the most, have more 
positive reviews. Also take a note at the people that didn't review the base
game (2037 out of 3644 DLC reviews, *59.9%*).


### Reviews by games owned

Another piece of data that might offer some insights is the difference between 
players owning different number of games:

```{r, Reviews-by-games-owned, warning=FALSE}
#Players owning different number of games
reviews_cleared %>%
  mutate(gamesowned_group = case_when(
    (author.num_games_owned >= 0 & author.num_games_owned < 50) ~ "Less than 50 games owned",
    (author.num_games_owned >= 50 & author.num_games_owned < 100) ~ "Between 50 and 100 games owned",
    (author.num_games_owned >= 100 & author.num_games_owned < 150) ~ "Between 100 and 150 games owned",
    (author.num_games_owned >= 150) ~"150 and more games owned")) %>%
  group_by(gamesowned_group, game) %>% 
  mutate(review_count = n()) %>% 
  ungroup() %>% 
  group_by(gamesowned_group, game, voted_up, review_count) %>% 
  summarize(
    review_voted = n(),
  ) %>% 
  as_tibble() %>% 
  mutate(percentage = review_voted/review_count) %>% 
  select(gamesowned_group, game, voted_up, percentage) %>% 
  #Putting the plot
  ggplot(aes(x = gamesowned_group, y  = percentage, fill = factor(voted_up))) + 
  geom_col(
    position="stack") +
  labs(
    x = "Playtime",
    y = "Percentage",
    title = "Reviews by games owned",
    subtitle = "Number of games owned by reviewers"
  ) + 
  scale_fill_discrete(name = "Review:", labels=c("Negative", "Positive")) + 
  scale_y_continuous(labels=scales::percent) + 
  #Adding labels
  geom_text(
    aes(label = percent(percentage,accuracy = 0.01)),
    position = position_fill(vjust = 0.5),
    size = 3
  ) + 
  scale_x_discrete(labels = (\(x) gsub("([^\\s]+\\s[^\\s]+)\\s","\\1\n",x,perl=TRUE)))  + 
  theme(axis.text.x = element_text(vjust = 0.5, hjust=0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~game, ncol = 1)

```
While this stat is interesting, the difference doesn't seem to be big enough
for any insights. It might be interesting to analyse the reviewers profiles 
for what games they own though.

### Reviews by total number of reviews written:

Also, let's see how review scores differ between the active/inactive review writers:

```{r, Reviews-by-total-numbe-of-reviews, warning=FALSE}
#Reviews by the player writing activities
reviews_cleared %>%
  mutate(reviews_group = case_when(
    (author.num_reviews >= 0 & author.num_reviews < 10) ~ "Less than 10 games reviewed",
    (author.num_reviews >= 10 & author.num_reviews < 50) ~ "Between 10 and 50 games reviewed",
    (author.num_reviews >= 50) ~"50 and more games reviewed")) %>%
  group_by(reviews_group, game) %>% 
  mutate(review_count = n()) %>% 
  ungroup() %>% 
  group_by(reviews_group, game, voted_up, review_count) %>% 
  summarize(
    review_voted = n(),
  ) %>% 
  as_tibble() %>% 
  mutate(percentage = review_voted/review_count) %>% 
  select(reviews_group, game, voted_up, percentage) %>% 
  #Putting the plot
  ggplot(aes(x = reviews_group, y  = percentage, fill = factor(voted_up))) + 
  geom_col(
    position="stack") +
  labs(
    x = "Playtime",
    y = "Percentage",
    title = "Reviews by total reviews written",
    subtitle = "Number of reviews written by reviewers"
  ) + 
  scale_fill_discrete(name = "Review:", labels=c("Negative", "Positive")) + 
  scale_y_continuous(labels=scales::percent) + 
  #Adding labels
  geom_text(
    aes(label = percent(percentage,accuracy = 0.01)),
    position = position_fill(vjust = 0.5),
    size = 3
  ) + 
  scale_x_discrete(labels = (\(x) gsub("([^\\s]+\\s[^\\s]+)\\s","\\1\n",x,perl=TRUE)))  + 
  theme(axis.text.x = element_text(vjust = 0.5, hjust=0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~game, ncol = 1)
```

It seems we have an interesting correlation here - players that have the 
higher number of reviews see the base game more negatively, while the
opposite is true for the DLC. This might indicate the players are more 
dissatisfied enough to write the negative review for the first time.

## Review word frequency analysis

First I'll tokenize the review texts for both the base game and the DLC using
unnest_tokens from the tidytext package and remove the stop words. I've
selected only English language since it's the largest language group and 
it's not possible to analyze the frequencies properly across multiple languages.

```{r, Word-frequency-tokenization, warning=FALSE, include=FALSE}
game_freq_pos <- basegame_cleared %>%
  ungroup() %>% 
  filter(language == "english") %>% 
  filter(nchar(review_text, type="chars") > 0) %>%
  select(review_id,voted_up,timestamp_created,review_text) %>% 
  unnest_tokens(review_words, review_text) %>% 
  anti_join(as_tibble(stopwords("en")),by=c("review_words" = "value"))

dlc_freq_pos <- dlc_cleared %>%
  ungroup() %>% 
  filter(language == "english") %>% 
  filter(nchar(review_text, type="chars") > 0) %>%
  select(review_id,voted_up,timestamp_created,review_text) %>% 
  unnest_tokens(review_words, review_text) %>% 
  anti_join(as_tibble(stopwords("en")),by=c("review_words" = "value"))
```

### Word clouds for positive and negative reviews for the base game and the dlc:

Base game:

```{r, Word-cloud-for-base-game, warning=FALSE}
set.seed(1)
#Base game
#Grouping up and counting
game_freq_pos %>%
  mutate(review_group = case_when(
    (voted_up == TRUE) ~ "Positive reviews",
    (voted_up == FALSE) ~ "Negative reviews")) %>%
  group_by(review_group) %>% 
  count(review_words, sort = TRUE) %>%
  rename(word_count = n) %>% 
  mutate(count_normalise = word_count/sum(word_count)) %>% 
  slice_max(count_normalise,n = 50, with_ties = FALSE) %>% 
  as_tibble() %>% 
  #makig plot
  ggplot(aes(label = review_words,
             color = review_group,
             size = count_normalise,
             alpha = count_normalise
  )
  ) +
  geom_text_wordcloud_area() + 
  labs(
    title = "Word cloud for the base game",
    caption = "Created using tidytext tokenization"
  ) +
  scale_size_area(max_size = 20) +
  theme_minimal() +
  scale_alpha_continuous(range = c(0.6,1)) +
  scale_fill_brewer(palette = "Set1"
                    , name = "review_group") +
  facet_wrap(~review_group)
```

And DLC:

```{r, Word-cloud-for-the-DLC, warning=FALSE}
set.seed(1)
#Base game
#Grouping up and counting
dlc_freq_pos %>%
  mutate(review_group = case_when(
    (voted_up == TRUE) ~ "Positive reviews",
    (voted_up == FALSE) ~ "Negative reviews")) %>%
  group_by(review_group) %>% 
  count(review_words, sort = TRUE) %>%
  rename(word_count = n) %>% 
  mutate(count_normalise = word_count/sum(word_count)) %>% 
  slice_max(count_normalise,n = 50, with_ties = FALSE) %>% 
  as_tibble() %>% 
  #makig plot
  ggplot(aes(label = review_words,
             color = review_group,
             size = count_normalise,
             alpha = count_normalise
  )
  ) +
  geom_text_wordcloud_area() + 
  labs(
    title = "Word cloud for the Crusader Kings III: Royal Court",
    caption = "Created using tidytext tokenization"
  ) +
  scale_size_area(max_size = 20) +
  theme_minimal() +
  scale_alpha_continuous(range = c(0.6,1)) +
  scale_fill_brewer(palette = "Set1"
                    , name = "review_group") +
  facet_wrap(~review_group)
```

While a lot of words are repeated both for the base game and DLC, there are
some things to notice. For example, price is mentioned in the multiple ways
("price", "overpriced", "30", etc.). Let's do a more detailed analysis for 
sentiment for keywords using sentimentr package.

### Sentiment analysis:

Overall, the workflow I used is this: Set keywords to filter sentences by -\> 
Filter out reviews without a text -\> Tokenize reviews by sentences -\> 
Filter out sentences not containing keywords -\> Apply sentimentr to get 
average sentiment for sentences -\> Filter out sentiment equal to zero -\> 
Make charts for sentiments for the base game and the DLC. Keep in mind, the 
final selection of the reviews with all of the filters applied is not very
big (721 reviews for the DLC and 5045 for the base game).

Let's take a look at the number of words that appear in the reviews for both games.
```{r, review_wordcounts}
reviews_wordcount <- inner_join(dlc_freq_pos %>%
                      unique() %>% 
                      count(review_words), 
                      game_freq_pos %>%
                      unique() %>% 
                      count(review_words), by = "review_words") %>% 
  mutate(min_word_count = pmin(n.x, n.y)) %>% 
  select(review_words, min_word_count) %>% 
  filter(min_word_count > 5) %>% 
  arrange(desc(min_word_count))

reviews_wordcount %>% print()
```

I've selected the words that have a noticeable difference in sentiment between
positive/negative reviews and are relevant for the analysis. As I said earlier,
sadly the review selection is not very big and sentiment analysis might be biased.
```{r, Sentiment-analysis-tokenization-and-stats, warning=FALSE, include=FALSE}
#Setting the terms for sentiment analysis
game_terms <- c(
  "content",
  "price",
  "culture",
  "time",
  "mechanics",
  "events",
  "features", 
  "bugs",
  "map",
  "depth",
  "artifacts",
  "characters",
  "religion",
  "war",
  "world",
  "quality",
  "strategy")
#game_terms <- c("price", " ai", "map", "war", "diplomacy","music", "mechanics",
#                "bug", "graphics", " ui", "content", "events")
#Base Game
game_sentences <- basegame_cleared %>%
  ungroup() %>% 
  filter(language == "english") %>% 
  filter(nchar(review_text, type="chars") > 0) %>%
  select(review_id,voted_up,timestamp_created,review_text) %>% 
  unnest_tokens(review_sentence, review_text, token="sentences") %>% 
  filter(grepl(paste0(game_terms, collapse = "|"),review_sentence)) %>% 
  rowid_to_column("rowid")
#Getting sentiment scores and joining with review sentences
game_sentiments <- sentiment_by(game_sentences$review_sentence, game_sentences$rowid)
game_sentiments <- inner_join(game_sentiments, game_sentences)
#Spreading keywords
game_sentiments <- game_sentiments %>% 
  mutate(keywords = str_extract_all(review_sentence, paste(game_terms, collapse = "|")))
game_sentiments <- game_sentiments %>% 
  unnest(keywords) %>% 
  unique() %>% 
  mutate(game = "Crusader Kings III")
#Getting sentiments

#DLC
#Getting sentences
dlc_sentences <- dlc_cleared %>%
  ungroup() %>% 
  filter(language == "english") %>% 
  filter(nchar(review_text, type="chars") > 0) %>%
  select(review_id,voted_up,timestamp_created,review_text) %>% 
  unnest_tokens(review_sentence, review_text, token="sentences") %>% 
  filter(grepl(paste0(game_terms, collapse = "|"),review_sentence)) %>% 
  rowid_to_column("rowid")
#Getting sentiment scores and joining with review sentences
dlc_sentiments <- sentiment_by(dlc_sentences$review_sentence, dlc_sentences$rowid)
dlc_sentiments <- inner_join(dlc_sentiments, dlc_sentences)
#Spreading keywords
dlc_sentiments <- dlc_sentiments %>% 
  mutate(keywords = str_extract_all(review_sentence, paste(game_terms, collapse = "|")))
dlc_sentiments <- dlc_sentiments %>% 
  unnest(keywords) %>% 
  unique() %>% 
  mutate(game = "Crusader Kings III: Royal Court")

game_sentiments <- rbind(dlc_sentiments, game_sentiments)
```

Making a plot for sentence sentiment for the base game and the DLC:

```{r, Base-game-sentiments, warning=FALSE}
game_sentiments %>% 
  filter(ave_sentiment != 0) %>% 
  group_by(voted_up,keywords, game) %>% 
  summarise(average_sentiment = median(ave_sentiment)) %>% 
  #Putting the plot
  ggplot(aes(x = keywords, y  = average_sentiment, fill = keywords)) + 
  lims(y = c(-0.5,0.5)) +
  geom_col(
    position="stack") +
  labs(
    x = NULL,
    y = "Average Sentiment",
    title = "Sentence sentiments",
    subtitle = "Sentence sentiments for selected keywords for the base game and the DLC",
    caption = "Created using sentimentr package"
  ) + 
  #Adding labels
  geom_text(
    aes(label = round(average_sentiment,2)),
    angle = 45,
    size = 3
  ) + 
  theme(axis.text.x = element_text(vjust = 0.5, hjust=0.5, angle=45),
        legend.position="none") +
  facet_wrap(~voted_up + game,
             labeller = labeller(
               voted_up = c( `TRUE` = "Positive Reviews",
                             `FALSE` = "Negative Reviews")
             ))
```

As we can see bugs, price, music and graphics are the ones that have the lowest 
median sentiment rates across the reviews of the DLC. This might indicate that 
players are dissatisfied by these aspects of this DLC.

### Exporting data for Tableau
```{r, Tableau-export, include=FALSE}
#For Windows, R 4.2.0+ is advised, otherwise UTF encoding might break
#Combined reviews csv
reviews_cleared %>%
  write.csv(paste0(c("data/tableau_reviews",".csv"), collapse=""), fileEncoding = "UTF-8", row.names = FALSE)
#Changed review opinion csv
reviews_cleared %>% 
  group_by(author.steamid) %>% 
  filter(n() == 2) %>% 
  select(author.steamid,game,voted_up) %>% 
  spread(game,voted_up) %>%
  rename(basegame_voteup = `Crusader Kings III`,
         dlc_voteup = `Crusader Kings III: Royal Court`) %>% 
  #grouping up and  getting percentages
  mutate(Vote_change = case_when(
    (basegame_voteup & dlc_voteup) ~ "Remained positive",
    (basegame_voteup==TRUE & dlc_voteup==FALSE) ~ "Changed from positive to negative",
    (basegame_voteup==FALSE & dlc_voteup==TRUE) ~ "Changed from negative to positive",
    (basegame_voteup==FALSE & dlc_voteup==FALSE) ~ "Remained negative",
  ))
  write.csv(paste0(c("data/tableau_opinionchange",".csv"), collapse=""), fileEncoding = "UTF-8", row.names = FALSE)
#combined game sentiments csv
game_sentiments %>%
  write.csv(paste0(c("data/tableau_sentiments",".csv"), collapse=""), fileEncoding = "UTF-8", row.names = FALSE)

game_wordcounts <- game_freq_pos %>%
  mutate(review_group = case_when(
    (voted_up == TRUE) ~ "Positive reviews",
    (voted_up == FALSE) ~ "Negative reviews")) %>%
  group_by(review_group) %>% 
  count(review_words, sort = TRUE) %>%
  rename(word_count = n) %>% 
  mutate(count_normalise = word_count/sum(word_count)) %>% 
  slice_max(count_normalise, n = 100, with_ties = FALSE) %>% 
  as_tibble() %>% 
  mutate(game= "Crusader Kings III")
dlc_wordcounts <- dlc_freq_pos %>%
  mutate(review_group = case_when(
    (voted_up == TRUE) ~ "Positive reviews",
    (voted_up == FALSE) ~ "Negative reviews")) %>%
  group_by(review_group) %>% 
  count(review_words, sort = TRUE) %>%
  rename(word_count = n) %>% 
  mutate(count_normalise = word_count/sum(word_count)) %>% 
  slice_max(count_normalise, n = 100, with_ties = FALSE) %>% 
  as_tibble() %>% 
  mutate(game= "Crusader Kings III: Royal Court")

#combined wordcount csv
write.csv(rbind(game_wordcounts,dlc_wordcounts),
          paste0(c("data/tableau_wordcounts",".csv"), collapse=""), fileEncoding = "UTF-8", row.names = FALSE)
```

## Notable insights


## Conclusions



## Proposed actions



## Further exploration


